---
title: "4_niche_breadth"
author: "JEON"
date: '2021 3 9 '
output: html_document
---
```{r}
library(ggcorrplot)
library(FactoMineR)
library(factoextra)
library(vegan)
library(listviewer)
library(MicroNiche)
library(corrr)
library(mapr)
library(ggplot2)
```

```{r}
library(tidyverse)

```

# Aims. 
Capture the niche breadth of every species.
Methodology include 3 ways,
1. classical Levin's Niche Breadth with my own function(다 더하는 것은 어렵. samp intensity에 대한 비판 방어는?)
2. Levin's Niche breadth with ENMeval
3. DBSCAN - 자의적 판단기준?
4. Broennimann et al. 2012 ecospat... var, PCA, Sum of Variance
5. 0.05 ~ 0.95 boxplot
6. 전문가 데이터와 비교 
7. 순위로 더하기
8. 다 해보고 순위가 비슷한 애들만 뽑아보기?
9. 


# 1. Classical Levin's niche breadth
This represent relative frequency of individuals in the jth Category
which catch the Eveness along the gradients

0 < B < J (number of Jth category)
0 represent specialist, J reprensent generalist.

until bio11, it is temperature. each category can be 2
from 12 - 19, they are precipitation. each category can be 10 each.

```{r}
data.reptile <- readr::read_rds(file = "data/data.reptile.rds")
```


```{r}

reaarange <- function(x){select(x@data, c(1,12,13,14,15,16,17,18,19,2,3,4,5,6,7,8,9,10,11))}

for (i in 1:length(data.mammal)){
data.mammal[[i]]@data <- reaarange(data.mammal[[i]])
}

for (i in 1:length(data.reptile)){
data.reptile[[i]]@data <- reaarange(data.reptile[[i]])
}
```


```{r}
library(raster)

bios.name <- paste0("C:/Users/lophital/Documents/rsac_x_overfit/bios/", list.files(pattern="*.tif", path = "C:/Users/lophital/Documents/rsac_x_overfit/bios"))

bios <- list()
for (i in 1:length(bios.name)){
  bios[[i]] <- raster::raster(bios.name[i])
}

bio.min <- vector()
for (i in 1:19){
bio.min[i] <- ceiling(bios[[i]]@data@min)
}

bio.max <- vector()
for (i in 1:19){
bio.max[i] <- ceiling(bios[[i]]@data@max)
}

biobreak <- list()
for(i in 1:11){
biobreak[[i]] <- bio.min[i]:bio.max[i]
}
for(i in 12:19){
biobreak[[i]] <- (bio.min[i]:bio.max[i]*10)  
}

bchist <- function(x, y){hist(x, breaks = y)}
biohist_reptile <- list()
for (i in 1:94){
biohist_reptile[[i]] <- map2(data.reptile[[i]]@data, biobreak, bchist)
}

levin.nb <- function(x){
  1/sum((x$counts/sum(x$counts))^2)
  }

levin.nb_reptile <- list()
for(i in 1:length(data.reptile)){
levin.nb_reptile[[i]] <- map(biohist_reptile[[i]], levin.nb)
}

nichebreadth.df <- data.frame(bio1 = map_dbl(levin.nb_reptile, 1),
                              bio2 = map_dbl(levin.nb_reptile, 2),
                              bio3 = map_dbl(levin.nb_reptile, 3),
                              bio4 = map_dbl(levin.nb_reptile, 4),
                              bio5 = map_dbl(levin.nb_reptile, 5),
                              bio6 = map_dbl(levin.nb_reptile, 6),
                              bio7 = map_dbl(levin.nb_reptile, 7),
                              bio8 = map_dbl(levin.nb_reptile, 8),
                              bio9 = map_dbl(levin.nb_reptile, 9),
                              bio10 = map_dbl(levin.nb_reptile, 10),
                              bio11 = map_dbl(levin.nb_reptile, 11),
                              bio12 = map_dbl(levin.nb_reptile, 12),
                              bio13 = map_dbl(levin.nb_reptile, 13),
                              bio14 = map_dbl(levin.nb_reptile, 14),
                              bio15 = map_dbl(levin.nb_reptile, 15),
                              bio16 = map_dbl(levin.nb_reptile, 16),
                              bio17 = map_dbl(levin.nb_reptile, 17),
                              bio18 = map_dbl(levin.nb_reptile, 18),
                              bio19 = map_dbl(levin.nb_reptile, 19))

```

# 2. Levin's niche breadth with ENMeval

```{r}
library(RInSp)

a <- RInSp::import.RInSp(data.reptile[[2]]@data, data.type = "double")
b <- RInSp::like.Wi(a)
```


# 3. Broennimann et al. 2012

plot in 2 PC axis, Z axis of SDM, Kernel density smoothing

```{r}
library(ecospat)
ecospat::ecospat.grid
```










```{r}
map(out_reptile$gbif$data, map_ggplot)
```
```{r mapping occurences with mapr::mapggplot}
map(out_aves$gbif$data, map_ggplot)
mapr::map_ggplot(out_reptile$gbif$data$Terrapene_carolina, map = "usa", size = 1)
```

```{r standardized extracted points values}
standard <- function(x){scale(x, center = T, scale = T)}

standard_amphibian <- extract_spatial_amphibian_lapply %>%  map(.f = scale(., center = T, scale = T))
standard_amphibian <- map(extract_spatial_amphibian_lapply, standard) 
standard_amphibian_df <- map(standard_amphibian, as.data.frame)


```



```{r PCA extracted points with FactoMineR::PCA }
#----------------------------
# PCA extracted points
#----------------------------
list_PCA_mammal <- lapply(
  extract_spatial_mammal_lapply,
  function(x){
    PCA(x)
  }
)

list_PCA_reptile <- lapply(
  extract_spatial_reptile_lapply,
  function(x){
    PCA(x)
  }
)

list_PCA_amphibian <- lapply(
  extract_spatial_amphibian_lapply,
  function(x){
    PCA(x)
  }
)

list_PCA_aves <- lapply(
  extract_spatial_aves_furrr,
  function(x){
    PCA(x)
  }
)

```

```{r PCA extracted points from saved}
#----------------------------
# PCA extracted points - saved
#----------------------------
list_PCA_mammal <- lapply(
  extract_mammal_saved,
  function(x){
    PCA(x)
  }
)

list_PCA_reptile <- lapply(
  extract_reptile_saved,
  function(x){
    PCA(x)
  }
)

list_PCA_amphibian <- lapply(
  extract_spatial_amphibian_lapply,
  function(x){
    PCA(x)
  }
)

list_PCA_aves <- lapply(
  extract_aves_saved,
  function(x){
    PCA(x)
  }
)

```


```{r PCA for the standardized extracted points value}
list_PCA_amphibian_standard <- lapply(
  standard_amphibian,
  function(x){
    PCA(x)
  }
)

```

```{r caculating niche breadth}
#----------------------------
# Niche breadth - 0.05 ~ 0.95
#----------------------------

cord_out_1 <- list()
cord_out_2 <- list()

for (i in seq_along(1:length(list_PCA_mammal))){
  cord_out_1[[i]] <- quantile(list_PCA_mammal[[i]]$ind$coord[,1], c(0.05, .95))
  cord_out_2[[i]] <- quantile(list_PCA_mammal[[i]]$ind$coord[,2], c(0.05, .95))
}

cord_mammal_df_pc1 <- do.call(rbind, cord_out_1)
cord_mammal_df_pc2 <- do.call(rbind, cord_out_2)
nb_mammal_pc1_df <- abs(cord_mammal_df_pc1[,1]) + cord_mammal_df_pc1[,2]
nb_mammal_pc2_df <- abs(cord_mammal_df_pc2[,2]) + cord_mammal_df_pc2[,2]
nb_mammal <- nb_mammal_pc1_df + nb_mammal_pc2_df 

##########################################################



cord_out_1 <- list()
cord_out_2 <- list()

for (i in seq_along(1:length(list_PCA_reptile))){
  cord_out_1[[i]] <- quantile(list_PCA_reptile[[i]]$ind$coord[,1], c(0.05, .95))
  cord_out_2[[i]] <- quantile(list_PCA_reptile[[i]]$ind$coord[,2], c(0.05, .95))
}

cord_reptile_df_pc1 <- do.call(rbind, cord_out_1)
cord_reptile_df_pc2 <- do.call(rbind, cord_out_2)
nb_reptile_pc1_df <- abs(cord_reptile_df_pc1[,1]) + cord_reptile_df_pc1[,2]
nb_reptile_pc2_df <- abs(cord_reptile_df_pc2[,2]) + cord_reptile_df_pc2[,2]
nb_reptile <- nb_reptile_pc1_df + nb_reptile_pc2_df

##########################################################

cord_out_1 <- list()
cord_out_2 <- list()
# A for loop to extract the quantiles and same
for (i in seq_along(1:length(list_PCA_amphibian))){
  cord_out_1[[i]] <- quantile(list_PCA_amphibian[[i]]$ind$coord[,1], c(0.05, .95))
  cord_out_2[[i]] <- quantile(list_PCA_amphibian[[i]]$ind$coord[,2], c(0.05, .95))
}

# Create two corresponding DF's
cord_amphibian_df_pc1 <- do.call(rbind, cord_out_1)
cord_amphibian_df_pc2 <- do.call(rbind, cord_out_2)
nb_amphibian_pc1_df <- abs(cord_amphibian_df_pc1[,1]) + cord_amphibian_df_pc1[,2]
nb_amphibian_pc2_df <- abs(cord_amphibian_df_pc2[,2]) + cord_amphibian_df_pc2[,2]
nb_amphibian <- nb_amphibian_pc1_df + nb_amphibian_pc2_df 

##########################################################

cord_out_1 <- list()
cord_out_2 <- list()
# A for loop to extract the quantiles and same
for (i in seq_along(1:length(list_PCA_aves))){
  cord_out_1[[i]] <- quantile(list_PCA_aves[[i]]$ind$coord[,1], c(0.05, .95))
  cord_out_2[[i]] <- quantile(list_PCA_aves[[i]]$ind$coord[,2], c(0.05, .95))
}

# Create two corresponding DF's
cord_aves_df_pc1 <- do.call(rbind, cord_out_1)
cord_aves_df_pc2 <- do.call(rbind, cord_out_2)
nb_aves_pc1_df <- abs(cord_aves_df_pc1[,1]) + cord_aves_df_pc1[,2]
nb_aves_pc2_df <- abs(cord_aves_df_pc2[,2]) + cord_aves_df_pc2[,2]
nb_aves <- nb_aves_pc1_df + nb_aves_pc2_df 

##########################################################
```

```{r niche breadth with standardzied}
#----------------------------
# Niche breadth with standardized 
#----------------------------

cord_out_1 <- list()
cord_out_2 <- list()

for (i in seq_along(1:length(list_PCA_amphibian_standard))){
  cord_out_1[[i]] <- quantile(list_PCA_amphibian_standard[[i]]$ind$coord[,1], c(0.05, .95))
  cord_out_2[[i]] <- quantile(list_PCA_amphibian_standard[[i]]$ind$coord[,2], c(0.05, .95))
}

cord_amphibian_df_pc1_sd <- do.call(rbind, cord_out_1)
cord_amphibian_df_pc2_sd <- do.call(rbind, cord_out_2)
nb_amphibian_pc1_df_sd <- abs(cord_amphibian_df_pc1_sd[,1]) + cord_amphibian_df_pc1_sd[,2]
nb_amphibian_pc2_df_sd <- abs(cord_amphibian_df_pc2_sd[,2]) + cord_amphibian_df_pc2_sd[,2]
nb_amphibian_sd <- nb_amphibian_pc1_df_sd + nb_amphibian_pc2_df_sd

```

Do really nb is different with taxons?

```{r save nb}
nb_aves_df <- data.frame(nb_aves)
nb_reptile_df <- data.frame(nb_reptile)
nb_mammal_df <- data.frame(nb_mammal)

write_csv(nb_aves_df, "E:/nichebreadth/nb_aves_df.csv")
write_csv(nb_reptile_df, "E:/nichebreadth/nb_reptile_df.csv")
write_csv(nb_mammal_df, "E:/nichebreadth/nb_mammal_df.csv")

```

```{r TOP 4 PCA Variables Visualize}
pca_var_g <- fviz_pca_var(pkmon_pca, select.var = list(cos2 = 0.5), repel = TRUE)

sweep(list_PCA_mammal$Peromyscus_maniculatus$var$coord,2,sqrt(list_PCA_mammal$Peromyscus_maniculatus$eig[1:ncol(list_PCA_mammal$Peromyscus_maniculatus$var$coord),1]),FUN="/")

pcm1 <- PCA(m1bio)
pca_var_contrib <- factoextra::fviz_pca_var(pcm1, select.var = list(contrib = 3), repel = TRUE)

```

```{r TOP 4 PCA Variables}
top4_pc1_mammal <- list()
top4_pc2_mammal <- list()
for (i in seq_along(1:length(list_PCA_mammal))){
 top4_pc1_mammal[[i]] <- names(tail(sort(list_PCA_mammal[[i]]$var$cos2[,1]), 4))
 top4_pc2_mammal[[i]] <- names(tail(sort(list_PCA_mammal[[i]]$var$cos2[,2]), 4))
}

top4_pc1_reptile <- list()
top4_pc2_reptile <- list()
for (i in seq_along(1:length(list_PCA_reptile))){
  top4_pc1_reptile[[i]] <- names(tail(sort(list_PCA_reptile[[i]]$var$cos2[,1]), 4))
  top4_pc2_reptile[[i]] <- names(tail(sort(list_PCA_reptile[[i]]$var$cos2[,2]), 4))
}

top4_pc1_amphibian <- list()
top4_pc2_amphibian <- list()
for (i in seq_along(1:length(list_PCA_amphibian))){
  top4_pc1_amphibian[[i]] <- names(tail(sort(list_PCA_amphibian[[i]]$var$cos2[,1]), 4))
  top4_pc2_amphibian[[i]] <- names(tail(sort(list_PCA_amphibian[[i]]$var$cos2[,2]), 4))
}

top4_pc1_aves <- list()
top4_pc2_aves <- list()
for (i in seq_along(1:length(list_PCA_aves))){
  top4_pc1_aves[[i]] <- names(tail(sort(list_PCA_aves[[i]]$var$cos2[,1]), 4))
  top4_pc2_aves[[i]] <- names(tail(sort(list_PCA_aves[[i]]$var$cos2[,2]), 4))
}

```

```{r TOP 4 PCA standardized variables}
##################### 
# TOP 4 PCA standardized 
######################
top4_pc1_amphibian_sd <- list()
top4_pc2_amphibian_sd <- list()
for (i in seq_along(1:length(list_PCA_amphibian_standard))){
  top4_pc1_amphibian_sd[[i]] <- names(tail(sort(list_PCA_amphibian_standard[[i]]$var$cos2[,1]), 4))
  top4_pc2_amphibian_sd[[i]] <- names(tail(sort(list_PCA_amphibian_standard[[i]]$var$cos2[,2]), 4))
}

```

```{r stacking rasters }

paste2 <- function(x){paste("E:/residual_sdm/" ,x, ".tif", sep = "")}



######################################################
top4_pc1_mammal.tif <- top4_pc1_mammal %>% map(paste2)
top4_pc2_mammal.tif <- top4_pc2_mammal %>% map(paste2)

top4_pc2_mammal.tif.stack <- top4_pc2_mammal.tif %>% map(stack)
top4_pc1_mammal.tif.stack <- top4_pc1_mammal.tif %>% map(stack)
top4_pc12_mammal.stack <- map2(top4_pc1_mammal.tif.stack, top4_pc2_mammal.tif.stack, stack)

##############################################################################
top4_pc1_reptile.tif <- top4_pc1_reptile %>% map(paste2)
top4_pc2_reptile.tif <- top4_pc2_reptile %>% map(paste2)

top4_pc2_reptile.tif.stack <- top4_pc2_reptile.tif %>% map(stack)
top4_pc1_reptile.tif.stack <- top4_pc1_reptile.tif %>% map(stack)
top4_pc12_reptile.stack <- map2(top4_pc1_reptile.tif.stack, top4_pc2_reptile.tif.stack, stack)

##############################################################################
top4_pc1_amphibian.tif <- top4_pc1_amphibian %>% map(paste2)
top4_pc2_amphibian.tif <- top4_pc2_amphibian %>% map(paste2)

top4_pc2_amphibian.tif.stack <- top4_pc2_amphibian.tif %>% map(stack)
top4_pc1_amphibian.tif.stack <- top4_pc1_amphibian.tif %>% map(stack)
top4_pc12_amphibian.stack <- map2(top4_pc1_amphibian.tif.stack, top4_pc2_amphibian.tif.stack, stack)

##############################################################################
top4_pc1_aves.tif <- top4_pc1_aves %>% map(paste2)
top4_pc2_aves.tif <- top4_pc2_aves %>% map(paste2)

top4_pc2_aves.tif.stack <- top4_pc2_aves.tif %>% map(stack)
top4_pc1_aves.tif.stack <- top4_pc1_aves.tif %>% map(stack)
top4_pc12_aves.stack <- map2(top4_pc1_aves.tif.stack, top4_pc2_aves.tif.stack, stack)

```

```{r get the extent}
#extent 
extent_mammal <- map(list_spatial_mammal, extent)
extent_reptile <- map(list_spatial_reptile, extent)
extent_amphibian <- map(list_spatial_amphibian, extent)
extent_aves <- map(list_spatial_aves, extent)
```

```{r}
#----------------------------
#raster crop to save times
#----------------------------

tic("mammal_bios") #mammal_bios: 5026.39 sec elapsed
mammal_bios <- furrr::future_map2(top4_pc12_mammal.stack, extent_mammal, crop)
toc()

tic("reptile_bios") #reptile_bios: 2834.84 sec elapsed
reptile_bios <- furrr::future_map2(top4_pc12_reptile.stack, extent_reptile, crop)
toc()

tic("amphibian_bios") #amphibian_bios: 762.35 sec elapsed
amphibian_bios <- furrr::future_map2(top4_pc12_amphibian.stack, extent_amphibian, crop)
toc()

tic("aves_bios") #aves_bios: 3765.14 sec elapsed
aves_bios <- furrr::future_map2(top4_pc12_aves.stack, extent_aves, crop)
toc()


```


```{r save raster}

reptile_bios %>% furrr::future_map2(paste0("J:/reptile_bios_", list_origin_reptile,".gri"), writeRaster)

amphibian_bios %>% furrr::future_map2(paste0("J:/amphibian_bios_", list_origin_amphibian,".gri"), writeRaster)

aves_bios %>% 
furrr::future_map2(paste0("J:/aves_bios_", list_origin_aves,".gri"), writeRaster)

```

```{r read saved rasters}

bios_mammal <- list.files(path = "J:/", pattern="*.gri")
bios_mammal <- paste0("J:/mammal_bios_", list_origin_mammal, ".gri")
bios_mammal <- map(bios_mammal, brick)

bios_amphibian <- list.files(path = "J:/", pattern="*.gri")
bios_amphibian <- paste0("J:/amphibian/amphibian_bios_", list_origin_amphibian, ".gri")
bios_amphibian <- map(bios_amphibian, brick)

bios_aves <- list.files(path = "J:/", pattern="*.gri")
bios_aves <- paste0("J:/aves_bios_", list_origin_aves, ".gri")
bios_aves <- map(bios_aves, brick)

bios_reptile <- list.files(path = "J:/", pattern="*.gri")
bios_reptile <- paste0("J:/reptile_bios_", list_origin_reptile, ".gri")
bios_reptile <- map(bios_reptile, brick)


```
Old face is name face. Classic PCA is nice as well.  


```{r}

```


t-SNE was fancy for last few years. Check it too.  

```{r}

```

But UMAP is even more fancier these days.

```{r}

```

Don't forget the environmental grid.
```{r}
dismo::gridSample()

```



```{r}

```

Before PCA, Let's check correlation matrix of variables
```{r}
extract_spatial_amphibian_lapply[[1]] %>% 
  mutate_if(is.numeric, scale) %>% 
  select_if(is.numeric) %>% 
  correlate() %>% # (2)
  shave(upper = TRUE) %>% # (3)
  stretch(na.rm = TRUE) %>% 
  arrange(-r) %>% 
  DT::datatable() %>% 
  DT::formatRound("r", digits = 2)

```


```{r}
dismo::threshold()
```

t-SNE, UMAP, PCA, Environment filter? 

## 추가 연구 Further study 
```{r}
library("sampbias")
```
