---
title: "6_SEVM"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(SDMtune)
library(blockCV)
library(ENMeval)
library(raster)
library(sf)
library(sp)
library(zeallot)
library(rJava)
library(dismo)
library(vegan)
```

```{r}
library(furrr)
future::plan(multisession, workers = 32)

```


데이터 가져오기
```{r 데이터 가져오기}
data.mammal <- readr::read_rds("data/newdata/data.mammal.rds")
data.reptile <- readr::read_rds(file = "data/newdata/data.reptile.rds")
data.amphibian <- readr::read_rds(file = "data/newdata/data.amphibian.rds")

```


거리 매트릭스 가져오기
```{r}
p.distm.3 <- readr::read_rds("D:/p.distm/p.distm.mammal.3.rds") 
p.distm.21 <- readr::read_rds("D:/p.distm/p.distm.mammal.21.rds")

a.distm.mammal <- readr::read_rds("distm/a.distm.mammal.rds")

p.distm.reptile <- readr::read_rds("distm/p.distm.reptile.rds")
p.distm.amphibian <- readr::read_rds("distm/p.distm.amphibian.rds")
a.distm.amphibian <- readr::read_rds("distm/a.distm.amphibian.rds")
```


```{r}

pcnm.p.reptile <- readr::read_rds("pcnm/pcnm.p.reptile.rds")
pcnm.a.reptile <- readr::read_rds("pcnm/pcnm.a.reptile.rds")

pcnm.p.amphibian <- readr::read_rds("pcnm/pcnm.p.amphibian.rds")
pcnm.a.amphibian <- readr::read_rds("pcnm/pcnm.a.amphibian.rds")
data.amphibian.copy <- data.amphibian
data.amphibian.copy <- data.amphibian.copy[-c(5,9,10,23,25,26,27,29,31,33,34,42,44,45,49)]

```


tooo big removeeee

```{r}
p.distm.21[c(5,8,11,12,14,17,19,21)] <- NULL
p.distm.21[c(3,5)] <- NULL
```



12turtle 48gecko 78
```{r}
p.distm.reptile[c(12,48,78)] <- NULL

```

?
```{r}
k <- vector()
for(i in 1:91){
  k[i] <- sum(data.reptile[[i]]@pa == 1)
}
which(k > 10000)
```

```{r}
p.distm.reptile[which(k > 10000)] <- NULL
data.reptile[which(k > 10000)] <- NULL
```


fuck above.

```{r}
data.reptile[which(num < 11000)] -> data.reptile
data.reptile <- map(data.reptile, addSamplesToBg)
```

```{r}
data.amphibian.copy <- map(data.amphibian.copy, addSamplesToBg)
#no don't... a matrix is original one.. no time to make new one
```



```{r}
p.reptile <- vector()
for(i in 1:length(data.reptile)){
p.reptile[i] <- sum(data.reptile[[i]]@pa == 1)} 

p.reptile
```
```{r}
p.amphibian <- vector()
for(i in 1:length(data.amphibian)){
p.amphibian[i] <- sum(data.amphibian[[i]]@pa == 1)} 

p.amphibian
```


```{r}
p.reptile.pcnm <- vector()
for(i in 1:length(pcnm.p.reptile)){
p.reptile.pcnm[i] <- nrow(pcnm.p.reptile[[i]]$vectors)}

p.reptile.pcnm
```

```{r}
p.amphibian.pcnm <- vector()
for(i in 1:length(pcnm.p.amphibian)){
p.amphibian.pcnm[i] <- nrow(pcnm.p.amphibian[[i]]$vectors)}

p.amphibian.pcnm
```


```{r}
for(i in 1:70){
  print(isTRUE(p.reptile.pcnm[i] == p.reptile[i]))
}
```

```{r}
for(i in 1:35){
  print(isTRUE(p.amphibian.pcnm[i] == p.amphibian[i]))
}
```


```{r}
a.reptile <- vector()
for(i in 1:length(data.reptile)){
a.reptile[i] <- sum(data.reptile[[i]]@pa == 0)} 

a.reptile
```
```{r}
a.reptile.pcnm <- vector()
for(i in 1:length(pcnm.p.reptile)){
a.reptile.pcnm[i] <- nrow(pcnm.a.reptile[[i]]$vectors)}

a.reptile.pcnm
```
```{r}
for(i in 1:70){
  print(isTRUE(a.reptile.pcnm[i] == a.reptile[i]))
}
```

```{r}
a.amphibian <- vector()
for(i in 1:length(data.amphibian.copy)){
a.amphibian[i] <- sum(data.amphibian.copy[[i]]@pa == 0)} 

a.amphibian
```
```{r}
a.amphibian.pcnm <- vector()
for(i in 1:length(pcnm.p.amphibian)){
a.amphibian.pcnm[i] <- nrow(pcnm.a.amphibian[[i]]$vectors)}

a.amphibian.pcnm
```
```{r}
for(i in 1:35){
  print(isTRUE(a.amphibian.pcnm[i] == a.amphibian[i]))
}
```



data.reptile and pcnm p a reptile is equal.

```{r}
library(FactoMineR)

PCA_reptile <- list()
for (i in 1:length(data.reptile)){
  PCA_reptile[[i]] <- PCA(data.reptile[[i]]@data, ncp = 19)
}

PCA_amphibian <- list()
for (i in 1:length(data.amphibian.copy)){
  PCA_amphibian[[i]] <- PCA(data.amphibian.copy[[i]]@data)
} 
```


```{r}

PCA12345_reptile <- list()
for(i in 1:length(PCA_reptile)){
  PCA12345_reptile[[i]] <- c(names(tail(sort(PCA_reptile[[i]]$var$cos2[,1]), 1)),
                            names(tail(sort(PCA_reptile[[i]]$var$cos2[,2]), 1)),
                            names(tail(sort(PCA_reptile[[i]]$var$cos2[,3]), 1)),
                            names(tail(sort(PCA_reptile[[i]]$var$cos2[,4]), 1)),
                            names(tail(sort(PCA_reptile[[i]]$var$cos2[,5]), 1))
                            )}



PCA12345_amphibian <- list()
for(i in 1:length(PCA_amphibian)){
  PCA12345_amphibian[[i]] <- c(names(tail(sort(PCA_amphibian[[i]]$var$cos2[,1]), 1)),
                             names(tail(sort(PCA_amphibian[[i]]$var$cos2[,2]), 1)),
                             names(tail(sort(PCA_amphibian[[i]]$var$cos2[,3]), 1)),
                             names(tail(sort(PCA_amphibian[[i]]$var$cos2[,4]), 1)),
                             names(tail(sort(PCA_amphibian[[i]]$var$cos2[,5]), 1)))}
```



```{r}
ncol.pcnm.p.reptile <- vector()
for(i in 1:length(pcnm.p.reptile)){
ncol.pcnm.p.reptile[i] <- ncol(pcnm.p.reptile[[i]]$vectors)
}

ncol.pcnm.a.reptile <- vector()
for(i in 1:length(pcnm.a.reptile)){
ncol.pcnm.a.reptile[i] <- ncol(pcnm.a.reptile[[i]]$vectors)
}

which(ncol.pcnm.p.reptile < 14)
which(ncol.pcnm.a.reptile < 14)
```
these shits will be thrown

```{r}
ncol.pcnm.p.amphibian <- vector()
for(i in 1:length(pcnm.p.amphibian)){
ncol.pcnm.p.amphibian[i] <- ncol(pcnm.p.amphibian[[i]]$vectors)
}

ncol.pcnm.a.amphibian <- vector()
for(i in 1:length(pcnm.a.amphibian)){
ncol.pcnm.a.amphibian[i] <- ncol(pcnm.a.amphibian[[i]]$vectors)
}

which(ncol.pcnm.p.amphibian < 14) #11 25 
which(ncol.pcnm.a.amphibian < 14) #21
```


```{r}
pcnm.a.reptile.copy <- pcnm.a.reptile
pcnm.p.reptile.copy <- pcnm.p.reptile

pcnm.p.reptile.copy <- pcnm.p.reptile.copy[-c(22, 27, 58, 60, 61)]
pcnm.a.reptile.copy <- pcnm.a.reptile.copy[-c(22, 27, 58, 60, 61)]
```


```{r}
pcnm.a.amphibian.copy <- pcnm.a.amphibian
pcnm.p.amphibian.copy <- pcnm.p.amphibian

pcnm.p.amphibian.copy <- pcnm.p.amphibian.copy[-c(11, 21, 25)]
pcnm.a.amphibian.copy <- pcnm.a.amphibian.copy[-c(11, 21, 25)]
```


cut pcnm vectors
```{r}
df.pcnm.reptile <- list()
for(i in 1:65){
as.data.frame(rbind(pcnm.p.reptile.copy[[i]]$vectors[,1:14],
                    pcnm.a.reptile.copy[[i]]$vectors[,1:14])) -> df.pcnm.reptile[[i]]}

```

```{r}
df.pcnm.amphibian <- list()
for(i in 1:32){
as.data.frame(rbind(pcnm.p.amphibian.copy[[i]]$vectors[,1:14],
                    pcnm.a.amphibian.copy[[i]]$vectors[,1:14])) -> df.pcnm.amphibian[[i]]}

```


```{r}
which(map_dbl(df.pcnm.reptile, ncol) != 14)

data.reptile.copy <- data.reptile
PCA12345_reptile.copy <- PCA12345_reptile
PCA_reptile.copy <- PCA_reptile

data.reptile.copy[-c(22, 27, 58, 60, 61)] -> data.reptile.copy
PCA12345_reptile.copy[-c(22, 27, 58, 60, 61)] -> PCA12345_reptile.copy
PCA_reptile.copy[-c(22, 27, 58, 60, 61)] -> PCA_reptile.copy

test <- list()
for(i in 1:65){
data.reptile.copy[[i]]@data %>% dplyr:::select(PCA12345_reptile.copy[[i]]) %>% cbind(df.pcnm.reptile[[i]]) -> test[[i]]}

which(map_dbl(test, ncol) != 19)
```
```{r}
which(map_dbl(df.pcnm.amphibian, ncol) != 14)

data.amphibian.copy2 <- data.amphibian.copy #주의 앰피는 렙타랑 조금 과정이 달랏음.
PCA12345_amphibian.copy <- PCA12345_amphibian
PCA_amphibian.copy <- PCA_amphibian

data.amphibian.copy2[-c(11, 21, 25)] -> data.amphibian.copy2 
PCA12345_amphibian.copy[-c(11, 21, 25)] -> PCA12345_amphibian.copy
PCA_amphibian.copy[-c(11, 21, 25)] -> PCA_amphibian.copy


test <- list()
for(i in 1:32){
data.amphibian.copy2[[i]]@data %>% dplyr:::select(PCA12345_amphibian.copy[[i]]) %>% cbind(df.pcnm.amphibian[[i]]) -> test[[i]]}

which(map_dbl(test, ncol) != 19) 
```



```{r}
#c( 4  8 13 16 18 20 21 34 35 37 41 42 47 48 52 53 59) overlapped.. 

PCA12345_reptile.copy[[4]]
names(tail(sort(PCA_reptile.copy[[4]]$var$cos2[,5])))
PCA12345_reptile.copy[[4]][5] <- "wc2.1_30s_bio_07"

PCA12345_reptile.copy[[8]]
names(tail(sort(PCA_reptile.copy[[8]]$var$cos2[,5])))
PCA12345_reptile.copy[[8]][5] <- "wc2.1_30s_bio_19"

PCA12345_reptile.copy[[13]]
names(tail(sort(PCA_reptile.copy[[13]]$var$cos2[,5])))
PCA12345_reptile.copy[[13]][5] <- "wc2.1_30s_bio_09"

PCA12345_reptile.copy[[16]]
names(tail(sort(PCA_reptile.copy[[16]]$var$cos2[,5])))
PCA12345_reptile.copy[[16]][5] <- "wc2.1_30s_bio_17"

PCA12345_reptile.copy[[18]]
names(tail(sort(PCA_reptile.copy[[18]]$var$cos2[,5])))
PCA12345_reptile.copy[[18]][5] <- "wc2.1_30s_bio_08"

PCA12345_reptile.copy[[20]]
names(tail(sort(PCA_reptile.copy[[20]]$var$cos2[,5])))
PCA12345_reptile.copy[[20]][5] <- "wc2.1_30s_bio_19"

PCA12345_reptile.copy[[21]]
names(tail(sort(PCA_reptile.copy[[21]]$var$cos2[,3])))
PCA12345_reptile.copy[[21]][3] <- "wc2.1_30s_bio_12"

PCA12345_reptile.copy[[34]]
names(tail(sort(PCA_reptile.copy[[34]]$var$cos2[,5])))
PCA12345_reptile.copy[[34]][5] <- "wc2.1_30s_bio_14"

PCA12345_reptile.copy[[35]]
names(tail(sort(PCA_reptile.copy[[35]]$var$cos2[,5])))
PCA12345_reptile.copy[[35]][5] <- "wc2.1_30s_bio_08"

PCA12345_reptile.copy[[37]]
names(tail(sort(PCA_reptile.copy[[37]]$var$cos2[,5])))
PCA12345_reptile.copy[[37]][5] <- "wc2.1_30s_bio_03"

PCA12345_reptile.copy[[41]]
names(tail(sort(PCA_reptile.copy[[41]]$var$cos2[,5])))
PCA12345_reptile.copy[[41]][5] <- "wc2.1_30s_bio_02"

PCA12345_reptile.copy[[42]]
names(tail(sort(PCA_reptile.copy[[42]]$var$cos2[,5])))
PCA12345_reptile.copy[[42]][5] <- "wc2.1_30s_bio_19"

PCA12345_reptile.copy[[47]]
names(tail(sort(PCA_reptile.copy[[47]]$var$cos2[,5])))
PCA12345_reptile.copy[[47]][5] <- "wc2.1_30s_bio_02"

PCA12345_reptile.copy[[48]]
names(tail(sort(PCA_reptile.copy[[48]]$var$cos2[,3])))
PCA12345_reptile.copy[[48]][3] <- "wc2.1_30s_bio_16"
names(tail(sort(PCA_reptile.copy[[48]]$var$cos2[,5])))
PCA12345_reptile.copy[[48]][5] <- "wc2.1_30s_bio_08"

PCA12345_reptile.copy[[52]]
names(tail(sort(PCA_reptile.copy[[52]]$var$cos2[,5])))
PCA12345_reptile.copy[[52]][5] <- "wc2.1_30s_bio_07"

PCA12345_reptile.copy[[53]]
names(tail(sort(PCA_reptile.copy[[53]]$var$cos2[,4])))
PCA12345_reptile.copy[[53]][4] <- "wc2.1_30s_bio_07"

PCA12345_reptile.copy[[59]]
names(tail(sort(PCA_reptile.copy[[59]]$var$cos2[,5])))
PCA12345_reptile.copy[[59]][5] <- "wc2.1_30s_bio_09"


for(i in 1:21){
data.reptile[[i]]@data %>% dplyr:::select(PCA12345_reptile[[i]]) %>% cbind(df.pcnm.reptile[[i]]) -> test[[i]]}

which(map_dbl(test, ncol) != 19)


```
```{r}
# c(1  2  5  8 13 22 23 24 25 28 31)


PCA12345_amphibian.copy[[1]]
names(tail(sort(PCA_amphibian.copy[[1]]$var$cos2[,5])))
PCA12345_amphibian.copy[[1]][5] <- "wc2.1_30s_bio_09"

PCA12345_amphibian.copy[[2]]
names(tail(sort(PCA_amphibian.copy[[2]]$var$cos2[,4])))
PCA12345_amphibian.copy[[2]][4] <- "wc2.1_30s_bio_18"

PCA12345_amphibian.copy[[5]]
names(tail(sort(PCA_amphibian.copy[[5]]$var$cos2[,4])))
PCA12345_amphibian.copy[[5]][4] <- "wc2.1_30s_bio_13"

PCA12345_amphibian.copy[[8]]
names(tail(sort(PCA_amphibian.copy[[8]]$var$cos2[,4])))
PCA12345_amphibian.copy[[8]][4] <- "wc2.1_30s_bio_18"

PCA12345_amphibian.copy[[13]]
names(tail(sort(PCA_amphibian.copy[[13]]$var$cos2[,5])))
PCA12345_amphibian.copy[[13]][5] <- "wc2.1_30s_bio_10"

PCA12345_amphibian.copy[[22]]
names(tail(sort(PCA_amphibian.copy[[22]]$var$cos2[,4])))
PCA12345_amphibian.copy[[22]][4] <- "wc2.1_30s_bio_03"

PCA12345_amphibian.copy[[23]]
names(tail(sort(PCA_amphibian.copy[[23]]$var$cos2[,5])))
PCA12345_amphibian.copy[[23]][5] <- "wc2.1_30s_bio_04"

PCA12345_amphibian.copy[[24]]
names(tail(sort(PCA_amphibian.copy[[24]]$var$cos2[,5])))
PCA12345_amphibian.copy[[24]][5] <- "wc2.1_30s_bio_04"

PCA12345_amphibian.copy[[25]]
names(tail(sort(PCA_amphibian.copy[[25]]$var$cos2[,5])))
PCA12345_amphibian.copy[[25]][5] <- "wc2.1_30s_bio_15"

PCA12345_amphibian.copy[[28]]
names(tail(sort(PCA_amphibian.copy[[28]]$var$cos2[,4])))
PCA12345_amphibian.copy[[28]][4] <- "wc2.1_30s_bio_08"

PCA12345_amphibian.copy[[31]]
names(tail(sort(PCA_amphibian.copy[[31]]$var$cos2[,5])))
PCA12345_amphibian.copy[[31]][5] <- "wc2.1_30s_bio_03"


test <- list()
for(i in 1:32){
data.amphibian.copy2[[i]]@data %>% dplyr:::select(PCA12345_amphibian.copy[[i]]) %>% cbind(df.pcnm.amphibian[[i]]) -> test[[i]]}

which(map_dbl(test, ncol) != 19) 

```







```{r}
for(i in 1:65){
print(isTRUE(nrow(test[[i]]) == nrow(data.reptile.copy[[i]]@data)))}

for(i in 1:65){
print(isTRUE(ncol(test[[i]]) == ncol(data.reptile.copy[[i]]@data)))}


```
```{r}
for(i in 1:32){
print(isTRUE(nrow(test[[i]]) == nrow(data.amphibian.copy2[[i]]@data)))}

for(i in 1:32){
print(isTRUE(ncol(test[[i]]) == ncol(data.amphibian.copy2[[i]]@data)))}


```


```{r CONFIRM}
for(i in 1:65){
data.reptile.copy[[i]]@data <- test[[i]]}

for(i in 1:65){
  print(dim(data.reptile.copy[[i]]@data))
}


```
```{r CONFIRM}
for(i in 1:32){
data.amphibian.copy[[i]]@data <- test[[i]]}

for(i in 1:32){
  print(dim(data.yyyy.copy[[i]]@data))
}


```{r}
write_rds(data.reptile.copy, "data/newdata/data.pcnm.reptile.rds")
```




















```{r}
#21 got less pcnm col, p got 2010col, a got 8col
for(i in 22:35){
as.data.frame(rbind(pcnm.p.amphibian[[i]]$vectors,
pcnm.a.amphibian[[i]]$vectors[,1:ncol(pcnm.p.amphibian[[i]]$vectors)])) -> k[[i]]}
```





amphibian. higher than 10k is

```{r}
k <- vector()
for(i in 1:50){
  k[i] <- sum(data.amphibian[[i]]@pa == 1)
}
which(k > 10000)
```




```{r}
p.distm.amphibian[c(5,9,10,23,25,26,27,29,31,33,34,42,44,45,49)] <- NULL
a.distm.amphibian[c(5,9,10,23,25,26,27,29,31,33,34,42,44,45,49)] <- NULL
```

```{r}
memory.limit(999999999)
```

```{r}
pcnm.p.reptile <- furrr::future_map(p.distm.reptile, 
                                      pcnm, 
                                      .options = furrr_options(seed = TRUE), 
                                      .progress = T)
#됬다 ㅠㅠ
pcnm.a.reptile <- furrr::future_map(a.distm.reptile,
                                      pcnm,
                                      .options = furrr_options(seed = TRUE), 
                                      .progress = T)

```


```{r}
pcnm.p.amphibian <- furrr::future_map(p.distm.amphibian, 
                                      pcnm, 
                                      .options = furrr_options(seed = TRUE), 
                                      .progress = T)
#됬다 ㅠㅠ
pcnm.a.amphibian <- furrr::future_map(a.distm.amphibian,
                                      pcnm,
                                      .options = furrr_options(seed = TRUE), 
                                      .progress = T)

```
PCNM 6, data.mammal 10 Macaca fascicularis just got 9 vecotr



```{r}
pcnm.p.mammal <- list()
for(i in 1:length(p.distm.3)){
pcnm.p.mammal[[i]] <- vegan::pcnm(p.distm.3[[i]])  
}

pcnm.p.mammal <- list()
for(i in 5:length(p.distm.21)){
pcnm.p.mammal[[i]] <- vegan::pcnm(p.distm.21[[i]])  
}

```
```{r}
pcnm.a.mammal <- list()
for(i in 1:length(p.distm.3)){
pcnm.a.mammal[[i]] <- vegan::pcnm(a.distm.mammal[[i]])  
}
```




```{r}

pcnm.p.reptile <- list()
for(i in 1:length(p.distm.reptile)){
pcnm.p.reptile[[i]] <- vegan::pcnm(p.distm.reptile[[i]])  
}

pcnm.p.reptile <- furrr::future_map(p.distm.reptile, pcnm, 
                                    .options = furrr_options(seed = TRUE), .progress = T)
```

```{r}
p.distm.amphibian <- readr::read_rds("distm/p.distm.amphibian.rds")
pcnm.p.amphibian <- list()
for(i in 1:length(p.distm.amphibian)){
pcnm.p.amphibian[[i]] <- vegan::pcnm(p.distm.amphibian[[i]])  
}
```






```{r}
model_rndcv4k_amphibian <- read_rds("model/newmodel/model_rndcv4k_amphibian.rds")
model_rndcv4k_amphibian[c(5,9,10,23,25,26,27,29,31,33,34,42,44,45,49)] <- NULL

data.amphibian <- read_rds("data/newdata/data.amphibian.rds")
data.amphibian[c(5,9,10,23,25,26,27,29,31,33,34,42,44,45,49)] <- NULL

```


만들어진 PCNM 가져오기 reptile
```{r} 
pcnm.a.reptile <- readr::read_rds("pcnm/pcnm.a.reptile.rds")
pcnm.p.reptile <- readr::read_rds("pcnm/pcnm.p.reptile.rds")
```




```{r}
my.ncol <- function(x){ncol(x$vectors)}
my.nrow <- function(x){nrow(x$vectors)}

map_int(pcnm.a.reptile, my.ncol) -> ncol.a.reptile
map_int(pcnm.p.reptile, my.ncol) -> ncol.p.reptile

map_int(pcnm.a.reptile, my.nrow) -> nrow.a.reptile
map_int(pcnm.p.reptile, my.nrow) -> nrow.p.reptile

which(ncol.a.reptile < 19) #58
which(ncol.p.reptile < 19) #8, 25, 53, 56, 58, 59

pcnm.a.amphibian[c(11, 21, 25)] <- NULL
pcnm.p.amphibian[c(11, 21, 25)] <- NULL
data.amphibian[c(11, 21, 25)] <- NULL
```

```{r}
nrow.ap.reptile
```

```{r}
nrow.data.reptile
```
```{r}
nrow.p.reptile

```
```{r}
my.nrow3 <- function(x){nrow(x@data[x@pa == 1,])}
my.nrow4 <- function(x){nrow(x@data[x@pa == 0,])}

nrow.p.data.reptile <- map_int(data.reptile, my.nrow3)
nrow.a.data.reptile <- map_int(data.reptile, my.nrow4)
```

```{r}
df.data.p <- data.frame(id = 1:length(nrow.p.data.reptile),
                        nrow = nrow.p.data.reptile)
df.pcnm.p <- data.frame(id = 1:length(nrow.p.reptile),
                        nrow = nrow.p.reptile)
df.pcnm.a <- data.frame(id = 1:length(nrow.a.reptile),
                        nrow = nrow.a.reptile)
df.data.a <- data.frame(id = 1:length(nrow.a.data.reptile),
                        nrow = nrow.a.data.reptile)
inner_join(df.pcnm.p, df.data.p, by = "nrow")
```

```{r}
inner_join(df.pcnm.a, df.data.p, by = "nrow")
```




```{r}
nrow.a.reptile + nrow.p.reptile -> nrow.ap.reptile
df.pcnm <- data.frame(id.pcnm = 1:67,
                      nrow = nrow.ap.reptile)
df.data <- data.frame(id.data = 1:91,
                      nrow = nrow.data.reptile)

dplyr::inner_join(df.data, df.pcnm, by = "nrow")

```

```{r}
my.nrow2 <- function(x){nrow(x@data)}
map_int(data.reptile, my.nrow2) -> nrow.data.reptile


```

```{r}
for(i in 1:67){which(nrow.ap.reptile[i] == nrow.data.reptile[i])}
```





```{r}
k <- list()
for(i in 1:20){
as.data.frame(rbind(pcnm.p.amphibian[[i]]$vectors,
pcnm.a.amphibian[[i]]$vectors[,1:ncol(pcnm.p.amphibian[[i]]$vectors)])) -> k[[i]]}
#21 got less pcnm col, p got 2010col, a got 8col
for(i in 22:35){
as.data.frame(rbind(pcnm.p.amphibian[[i]]$vectors,
pcnm.a.amphibian[[i]]$vectors[,1:ncol(pcnm.p.amphibian[[i]]$vectors)])) -> k[[i]]}


```





```{r}
k <- list()
for(i in 1:20){
as.data.frame(rbind(pcnm.p.amphibian[[i]]$vectors,
pcnm.a.amphibian[[i]]$vectors[,1:ncol(pcnm.p.amphibian[[i]]$vectors)])) -> k[[i]]}
#21 got less pcnm col, p got 2010col, a got 8col
for(i in 22:35){
as.data.frame(rbind(pcnm.p.amphibian[[i]]$vectors,
pcnm.a.amphibian[[i]]$vectors[,1:ncol(pcnm.p.amphibian[[i]]$vectors)])) -> k[[i]]}


```
too much vectors... 

# choose 16 in ratio
```{r}
k <- list()
for(i in 1:35){
as.data.frame(rbind(pcnm.p.amphibian[[i]]$vectors[,round(seq.int(1, ncol(pcnm.p.amphibian[[i]]$vectors), length.out =16))], 
pcnm.a.amphibian[[i]]$vectors[,round(seq.int(1, ncol(pcnm.a.amphibian[[i]]$vectors), length.out =16))])) -> k[[i]]}

```


PCNM p 11 got just 4 column. remove it.(among 35)
and again, pcnm a 20 got 8 column
```{r}

pcnm.p.ncol <- vector()
for(i in 1:35){
  ncol(pcnm.p.amphibian[[i]]$vectors) -> pcnm.p.ncol[i]
}

pcnm.a.ncol <- vector()
for(i in 1:35){
  ncol(pcnm.a.amphibian[[i]]$vectors) -> pcnm.a.ncol[i]
}

which(pcnm.a.ncol < 19) #21
which(pcnm.p.ncol < 19) #11, 25

pcnm.a.amphibian[c(11, 21, 25)] <- NULL
pcnm.p.amphibian[c(11, 21, 25)] <- NULL
data.amphibian[c(11, 21, 25)] <- NULL
```

```{r to show pcnm var imp}
pcnm.p.ncol <- vector()
for(i in 1:32){
  ncol(pcnm.p.amphibian[[i]]$vectors) -> pcnm.p.ncol[i]
}

pcnm.a.ncol <- vector()
for(i in 1:32){
  ncol(pcnm.a.amphibian[[i]]$vectors) -> pcnm.a.ncol[i]
}

which(pcnm.a.ncol < 50) #0
which(pcnm.p.ncol < 50) #28

pcnm.a.amphibian[28] <- NULL
pcnm.p.amphibian[28] <- NULL

```


# choose 16 in varsel
```{r}
k <- list()
for(i in 1:31){
as.data.frame(rbind(pcnm.p.amphibian[[i]]$vectors[,1:50], 
pcnm.a.amphibian[[i]]$vectors[,1:50])) -> k[[i]]}

```





```{r}
library(FactoMineR)

PCA_amphibian <- list()
for (i in 1:length(data.amphibian)){
  PCA_amphibian[[i]] <- PCA(data.amphibian[[i]]@data)
} 
```

```{r}
PCA123_amphibian <- list()
for(i in 1:length(PCA_amphibian)){
  PCA123_amphibian[[i]] <- c(names(tail(sort(PCA_amphibian[[i]]$var$cos2[,1]), 1)),
                       names(tail(sort(PCA_amphibian[[i]]$var$cos2[,2]), 1)),
                       names(tail(sort(PCA_amphibian[[i]]$var$cos2[,3]), 1)))}

PCA123_amphibian[c(11, 21, 25)] <- NULL
PCA123_amphibian[c(28)] <- NULL

for(i in 1:10){
data.amphibian[[i]]@data %>% dplyr:::select(PCA123_amphibian[[i]]) %>% cbind(k[[i]]) -> k[[i]]}




data.amphibian.test <- data.amphibian


for(i in 1:10){
data.amphibian.test[[i]]@data <- k[[i]]}

t.t.amphibian_0.2.test <- list()
for (i in 1:10){
  t.t.amphibian_0.2.test[[i]] <- trainValTest(data.amphibian.test[[i]], 
                                         test = 0.2, 
                                         only_presence = TRUE, 
                                         seed = 1)}
```


```{r}
rnd4k <- function(x){randomFolds(x[[1]], 
                                 k = 4,
                                 only_presence = TRUE,
                                 seed = 1)}

folds.rnd4k_amphibian.test <- map(t.t.amphibian_0.2.test, rnd4k)
```

t.t.amp 10 got glm error

```{r}
t.t.amphibian_0.2.test <- t.t.amphibian_0.2.test[-10] 
folds.rnd4k_amphibian.test <- folds.rnd4k_amphibian.test[-10] 
```

after remove 10, still error
```{r}
t.t.amphibian_0.2.test <- t.t.amphibian_0.2.test[-22] 
folds.rnd4k_amphibian.test <- folds.rnd4k_amphibian.test[-22] 
```

```{r}
model_rndcv4k_amphibian <- future_map2(t.t.amphibian_0.2.test, 
                                    folds.rnd4k_amphibian.test, 
                                    maxnet.train, 
                                    .options = furrr_options(seed = TRUE),
                                    .progress = T)
```

```{r}
folds.sp4k_amphibian <- readr::read_rds("folds/folds.sp4k_amphibian.rds")
folds.sp4k_amphibian[c(5,9,10,23,25,26,27,29,31,33,34,42,44,45,49)] <- NULL
folds.sp4k_amphibian[c(11, 21, 25)] <- NULL
folds.sp4k_amphibian <- folds.sp4k_amphibian[-10] 
folds.sp4k_amphibian <- folds.sp4k_amphibian[-22] 
```


```{r}
model_spcv4k_amphibian <- future_map2(t.t.amphibian_0.2.test, 
                                    folds.sp4k_amphibian, 
                                    maxnet.train, 
                                    .options = furrr_options(seed = TRUE),
                                    .progress = T)
```


```{r}
b <- SDMtune::varSel(maxent.a1@models[[1]], metric = "auc",test = maxent.a1@models[[1]]@data, bg4cor = data.amphibian.test[[1]])
c <- SDMtune:::varImp(maxent.a1)

SDMtune::
```


```{r}
# Acquire environmental variables
files <- list.files(path = file.path(system.file(package = "dismo"), "ex"),
                    pattern = "grd", full.names = TRUE)
predictors <- raster::stack(files)

# Prepare presence and background locations
p_coords <- virtualSp$presence
bg_coords <- virtualSp$background

# Create SWD object
data <- prepareSWD(species = "Virtual species", p = p_coords, a = bg_coords,
                   env = predictors, categorical = "biome")

# Split presence locations in training (80%) and testing (20%) datasets
datasets <- trainValTest(data, test = 0.2, only_presence = TRUE)
train <- datasets[[1]]
test <- datasets[[2]]

# Train a model
model <- train(method = "Maxnet", data = train, fc = "l")

# Prepare background locations to test autocorrelation, this usually gives a
# warning message given that less than 10000 points can be randomly sampled
bg_coords <- dismo::randomPoints(predictors, 10000)
bg <- prepareSWD(species = "Virtual species", a = bg_coords,
                 env = predictors, categorical = "biome")

## Not run: 
# Remove variables with correlation higher than 0.7 accounting for the AUC,
# in the following example the variable importance is computed as permutation
# importance
vs <- varSel(model, metric = "auc", bg4cor = bg, test = test, cor_th = 0.7,
             permut = 1)
vs

# Remove variables with correlation higher than 0.7 accounting for the TSS,
# in the following example the variable importance is the MaxEnt percent
# contribution
# Train a model
# The next line checks if Maxent is correctly configured but you don't need
# to run it in your script
if (dismo::maxent(silent = TRUE)) {
model <- train(method = "Maxent", data = train, fc = "l")
vs <- varSel(model, metric = "tss", bg4cor = bg, test = test, cor_th = 0.7,
             use_pc = TRUE)
vs

# Remove variables with correlation higher than 0.7 accounting for the aicc,
# in the following example the variable importance is the MaxEnt percent
# contribution
vs <- varSel(model, metric = "aicc", bg4cor = bg, cor_th = 0.7,
             use_pc = TRUE, env = predictors)
vs
}

## End(Not run)
```


