---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# is pcnm varaible importance high as sequence?

```{r}
library(tidyverse)
library(SDMtune)
library(blockCV)
library(ENMeval)
library(raster)
library(sf)
library(sp)
library(zeallot)
library(rJava)
library(dismo)
```
```{r}
library(furrr)
future::plan(multisession, workers = 31)
stopCluster(cl)
```


load models
```{r}
model_rndcv4k_reptile <- readr::read_rds("model/newmodel/model_rndcv4k_reptile.rds")
model_spcv4k_reptile <- readr::read_rds("model/newmodel/model_spcv4k_reptile.rds")


model_rndcv4k.pcnm_reptile <- readr::read_rds("model/newmodel/model_pcnm/model_rndcv4k_reptile.rds")
model_spcv4k.pcnm_reptile <- readr::read_rds("model/newmodel/model_pcnm/model_spcv4k_reptile.rds")

model_rndcv4k_amphibian <- readr::read_rds("model/newmodel/model_rndcv4k_amphibian.rds")
model_spcv4k_amphibian <- readr::read_rds("model/newmodel/model_spcv4k_amphibian.rds")

#PCNMs
model_rndcv4k.pcnm_amphibian <- readr::read_rds("model/newmodel/model_pcnm/model_rndcv4k_amphibian.rds")
model_spcv4k.pcnm_amphibian <- readr::read_rds("model/newmodel/model_pcnm/model_spcv4k_amphibian.rds")

t.t.mammal_0.2 <- readr::read_rds("t.t/newt.t/t.t.mammal_0.2.rds")
t.t.reptile_0.2 <- readr::read_rds("t.t/newt.t/t.t.reptile_0.2.rds")
t.t.amphibian_0.2 <- readr::read_rds("t.t/newt.t/t.t.amphibian_0.2.rds")

t.t.pcnm.reptile_0.2 <- readr::read_rds("t.t/newt.t/t.t.pcnm.reptile_0.2.rds")
t.t.pcnm.amphibian_0.2 <- readr::read_rds("t.t/newt.t/t.t.pcnm.amphibian_0.2.rds")
```


varimp

```{r}

varimp_rndcv4k_reptile <- map(model_rndcv4k_reptile, varImp)
varimp_rndcv4k_amphibian <- map(model_rndcv4k_amphibian, varImp)

varimp_rndcv4k.pcnm_amphibian <- map(model_rndcv4k.pcnm_amphibian, varImp)
varimp_rndcv4k.pcnm_reptile <- map(model_rndcv4k.pcnm_reptile, varImp)


# maxent varimp
maxentvarimp_rndcv4k.pcnm_reptile <- future_map(model_rndcv4k.pcnm_reptile, maxentVarImp, 
                                                .options = furrr_options(seed = TRUE), .progress = T)
write_rds(maxentvarimp_rndcv4k.pcnm_reptile, "maxentvarimp_rndcv4k.pcnm_reptile.rds")
maxentvarimp_rndcv4k.pcnm_amphibian <- future_map(model_rndcv4k.pcnm_amphibian, maxentVarImp, 
                                                .options = furrr_options(seed = TRUE), .progress = T)
write_rds(maxentvarimp_rndcv4k.pcnm_amphibian, "maxentvarimp_rndcv4k.pcnm_amphibian.rds")
maxentvarimp_spcv4k.pcnm_reptile <- future_map(model_spcv4k.pcnm_reptile, maxentVarImp,
                                               .options = furrr_options(seed = TRUE), .progress =  T)
write_rds(maxentvarimp_spcv4k.pcnm_reptile, "maxentvarimp_spcv4k.pcnm_reptile.rds")
maxentvarimp_spcv4k.pcnm_amphibian <- future_map(model_spcv4k.pcnm_amphibian, maxentVarImp,
                                               .options = furrr_options(seed = TRUE), .progress =  T)
write_rds(maxentvarimp_spcv4k.pcnm_amphibian, "maxentvarimp_spcv4k.pcnm_amphibian.rds")
# maxent varimp



varimp_spcv4k_reptile <- map(model_spcv4k_reptile, varImp)
varimp_spcv4k_amphibian <- map(model_spcv4k_amphibian, varImp)

varimp_spcv4k.pcnm_amphibian <- map(model_spcv4k.pcnm_amphibian, varImp)
varimp_spcv4k.pcnm_reptile <- map(model_spcv4k.pcnm_reptile, varImp)

df.maxentvarimp_rndcv4k.pcnm_reptile <- list()
for(i in 1:length(maxentvarimp_rndcv4k.pcnm_reptile)){
df.maxentvarimp_rndcv4k.pcnm_reptile[[i]] <- mutate(maxentvarimp_rndcv4k.pcnm_reptile[[i]], 
                                      taxa = "reptile", 
                                      species = model_rndcv4k.pcnm_reptile[[i]]@data@species,
                                      cv = "random")
}

df.maxentvarimp_rndcv4k.pcnm_amphibian <- list()
for(i in 1:length(maxentvarimp_rndcv4k.pcnm_amphibian)){
df.maxentvarimp_rndcv4k.pcnm_amphibian[[i]] <- mutate(maxentvarimp_rndcv4k.pcnm_amphibian[[i]],
                                        taxa = "amphibian",
                                        species = model_rndcv4k.pcnm_amphibian[[i]]@data@species,
                                        cv = "random")
}
df.maxentvarimp_spcv4k.pcnm_reptile <- list()
for(i in 1:length(maxentvarimp_spcv4k.pcnm_reptile)){
df.maxentvarimp_spcv4k.pcnm_reptile[[i]] <- mutate(maxentvarimp_spcv4k.pcnm_reptile[[i]],
                                        taxa = "reptile",
                                        species = model_spcv4k.pcnm_reptile[[i]]@data@species,
                                        cv = "spatial")
}
df.maxentvarimp_spcv4k.pcnm_amphibian <- list()
for(i in 1:length(maxentvarimp_spcv4k.pcnm_amphibian)){
df.maxentvarimp_spcv4k.pcnm_amphibian[[i]] <- mutate(maxentvarimp_spcv4k.pcnm_amphibian[[i]],
                                        taxa = "amphibian",
                                        species = model_spcv4k.pcnm_amphibian[[i]]@data@species,
                                        cv = "spatial")
}

# not use below
for(i in 1:length(varimp_spcv4k.pcnm_reptile)){
varimp_spcv4k.pcnm_reptile[[i]] <- mutate(varimp_spcv4k.pcnm_reptile[[i]],
                                           taxa = "reptile",
                                           species = model_spcv4k.pcnm_reptile[[i]]@data@species,
                                           cv = "random")
}
for(i in 1:length(varimp_spcv4k.pcnm_amphibian)){
varimp_spcv4k.pcnm_amphibian[[i]] <- mutate(varimp_rndcv4k.pcnm_amphibian[[i]],
                                        taxa = "amphibian",
                                        species = model_rndcv4k.pcnm_amphibian[[i]]@data@species,
                                        cv = "random")
}
for(i in 1:length(varimp_rndcv4k.pcnm_reptile)){
varimp_rndcv4k.pcnm_reptile[[i]] <- mutate(varimp_rndcv4k.pcnm_reptile[[i]],
                                           taxa = "reptile",
                                           species = model_rndcv4k.pcnm_reptile[[i]]@data@species,
                                           cv = "random")
}
for(i in 1:length(varimp_rndcv4k.pcnm_amphibian)){
varimp_rndcv4k.pcnm_amphibian[[i]] <- mutate(varimp_rndcv4k.pcnm_amphibian[[i]],
                                        taxa = "amphibian",
                                        species = model_rndcv4k.pcnm_amphibian[[i]]@data@species,
                                        cv = "random")
}
for(i in 1:length(varimp_spcv4k.pcnm_reptile)){
varimp_spcv4k.pcnm_reptile[[i]] <- mutate(varimp_spcv4k.pcnm_reptile[[i]],
                                           taxa = "reptile",
                                           species = model_spcv4k.pcnm_reptile[[i]]@data@species,
                                           cv = "spatial")
}
for(i in 1:length(varimp_spcv4k.pcnm_amphibian)){
varimp_spcv4k.pcnm_amphibian[[i]] <- mutate(varimp_spcv4k.pcnm_amphibian[[i]],
                                        taxa = "amphibian",
                                        species = model_spcv4k.pcnm_amphibian[[i]]@data@species,
                                        cv = "spatial")
}
for(i in 1:length(varimp_spcv4k.pcnm_reptile)){
varimp_spcv4k.pcnm_reptile[[i]] <- mutate(varimp_spcv4k.pcnm_reptile[[i]],
                                           taxa = "reptile",
                                           species = model_spcv4k.pcnm_reptile[[i]]@data@species,
                                           cv = "spatial")
}
for(i in 1:length(varimp_spcv4k.pcnm_amphibian)){
varimp_spcv4k.pcnm_amphibian[[i]] <- mutate(varimp_spcv4k.pcnm_amphibian[[i]],
                                        taxa = "amphibian",
                                        species = model_spcv4k.pcnm_amphibian[[i]]@data@species,
                                        cv = "spatial")
}

df.maxentvarimp_rndcv4k.pcnm_reptile <- do.call(rbind, df.maxentvarimp_rndcv4k.pcnm_reptile) 
df.maxentvarimp_rndcv4k.pcnm_amphibian <- do.call(rbind, df.maxentvarimp_rndcv4k.pcnm_amphibian) 
df.maxentvarimp_spcv4k.pcnm_reptile <- do.call(rbind, df.maxentvarimp_spcv4k.pcnm_reptile) 
df.maxentvarimp_spcv4k.pcnm_amphibian <- do.call(rbind, df.maxentvarimp_spcv4k.pcnm_amphibian) 

rbind(df.maxentvarimp_rndcv4k.pcnm_reptile,
      df.maxentvarimp_rndcv4k.pcnm_amphibian,
      df.maxentvarimp_spcv4k.pcnm_reptile,
      df.maxentvarimp_spcv4k.pcnm_amphibian) -> df.VARIMP

#this fucked up var name in bioclimates
gsub("PCNM1","PCNM01",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM2","PCNM02",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM3","PCNM03",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM4","PCNM04",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM5","PCNM05",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM6","PCNM06",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM7","PCNM07",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM8","PCNM08",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM9","PCNM09",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM010","PCNM10",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM011","PCNM11",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM012","PCNM12",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM013","PCNM13",  df.VARIMP$Variable) -> df.VARIMP$Variable
gsub("PCNM014","PCNM14",  df.VARIMP$Variable) -> df.VARIMP$Variable





ggplot(df.VARIMP) + 
  geom_boxplot(aes(x = Variable, y = Permutation_importance)) + 
  theme_light() +
  theme(strip.text.x = element_text(size = 9, colour = "black"),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        strip.background = element_rect(colour="gray",
                                        fill="white")) + 
  labs(title="Permutation variable importance", 
       subtitle="averaged decrease in training AUC",
       x="Variable",
       y="Variable Importance(normalized %)") -> plot.VARIMP_pt

ggplot(df.VARIMP) + 
  geom_boxplot(aes(x = Variable, y = Percent_contribution)) + 
  theme_light() +
  theme(strip.text.x = element_text(size = 9, colour = "black"),
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        strip.background = element_rect(colour="gray",
                                        fill="white")) + 
  labs(title="Percent contribution for variable importance", 
       subtitle="Based on regularized gain from each coefficient modifying iteration",
       x="Variable",
       y="Variable Importance") -> plot.VARIMP_pc

```


35 each

```{r}
pcnm.p.ncol <- vector()
for(i in 1:35){
  ncol(pcnm.p[[i]]$vectors) -> pcnm.p.ncol[i]
}

pcnm.a.ncol <- vector()
for(i in 1:35){
  ncol(pcnm.a[[i]]$vectors) -> pcnm.a.ncol[i]
}

which(pcnm.a.ncol < 50) #21
which(pcnm.p.ncol < 50) #11, 25, 31

pcnm.a[c(11, 21, 25, 31)] <- NULL
pcnm.p[c(11, 21, 25, 31)] <- NULL
#total 31pcs
```


makes them together
```{r}
pcnm.df <- list()
for(i in 1:31){
as.data.frame(rbind(pcnm.p[[i]]$vectors[,1:50],
                    pcnm.a[[i]]$vectors[,1:50])) -> pcnm.df[[i]]}
```

put them as variable
load data

```{r}
data <- readr::read_rds("data/newdata/data.amphibian.rds")
data[c(5,9,10,23,25,26,27,29,31,33,34,42,44,45,49)] <- NULL # make 35 same as pcnm
data[c(11, 21, 25, 31)] <- NULL
```


conduct PCA to cut climate variable into 3

```{r}
library(FactoMineR)

PCA_amphibian <- list()
for (i in 1:length(data)){
  PCA_amphibian[[i]] <- PCA(data[[i]]@data)
} 
```




make PCA123 to find best 3
```{r}
PCA123_amphibian <- list()
for(i in 1:length(PCA_amphibian)){
  PCA123_amphibian[[i]] <- c(names(tail(sort(PCA_amphibian[[i]]$var$cos2[,1]), 1)),
                       names(tail(sort(PCA_amphibian[[i]]$var$cos2[,2]), 1)),
                       names(tail(sort(PCA_amphibian[[i]]$var$cos2[,3]), 1)))}
```


put them inside of data
```{r}
for(i in 1:31){
data[[i]]@data %>% dplyr:::select(PCA123_amphibian[[i]]) %>% cbind(pcnm.df[[i]]) -> data[[i]]@data}
```


cut test
```{r}
t.t <- list()
for (i in 1:31){
  t.t[[i]] <- trainValTest(data[[i]], 
                                         test = 0.2, 
                                         only_presence = TRUE, 
                                         seed = 1)}
```


make rnd fold
```{r}
rnd4k <- function(x){randomFolds(x[[1]], 
                                 k = 4,
                                 only_presence = TRUE,
                                 seed = 1)}

folds.rnd4k_amphibian.test <- map(t.t, rnd4k)
```


do model
```{r}
maxnet.train <- function(x, y){SDMtune::train("Maxnet",
                                               data = x[[1]],
                                               folds = y)}

model_rndcv4k_amphibian <- future_map2(t.t, 
                                    folds.rnd4k_amphibian.test, 
                                    maxnet.train, 
                                    .options = furrr_options(seed = TRUE),
                                    .progress = T)
```

fix glm error
```{r}
maxnet.train(t.t[[10]], folds.rnd4k_amphibian.test[[10]]) #error
```
```{r}
SDMtune::addSamplesToBg(t.t[[10]][[1]])

SDMtune::train("Maxnet",
               data = SDMtune::addSamplesToBg(t.t[[10]][[1]]),
              folds = folds.rnd4k_amphibian.test[[10]]) #still error
```
```{r}
SDMtune::addSamplesToBg(data[[10]]) %>% trainValTest(., 
                                         test = 0.2, 
                                         only_presence = TRUE, 
                                         seed = 1) -> t.t.2


rnd4k(t.t.2) -> fold2

maxnet.train(t.t.2, fold2) # works!!!
```
DO MODEL AGAIN
```{r}
data2 <- map(data, addSamplesToBg)
t.t2 <- list()
for (i in 1:31){
  t.t2[[i]] <- trainValTest(data2[[i]], 
                                         test = 0.2, 
                                         only_presence = TRUE, 
                                         seed = 1)}
fold2 <- map(t.t2, rnd4k)


```

```{r}
model_rndcv4k_amphibian <- future_map2(t.t2, 
                                    fold2, 
                                    maxnet.train, 
                                    .options = furrr_options(seed = TRUE),
                                    .progress = T)
```




check variable importance
```{r}
varimp <- future_map(model_rndcv4k_amphibian, varImp)

varimp.df <- data.frame(matrix(ncol = 62, nrow = 19))
cbind(varimp[[1]][1:19,1:2],
      varimp[[2]][1:19,1:2],
      varimp[[3]][1:19,1:2],
      varimp[[4]][1:19,1:2],
      varimp[[5]][1:19,1:2],
      varimp[[6]][1:19,1:2],
      varimp[[7]][1:19,1:2],
      varimp[[8]][1:19,1:2],
      varimp[[9]][1:19,1:2],
      varimp[[10]][1:19,1:2],
      varimp[[11]][1:19,1:2],
      varimp[[12]][1:19,1:2],
      varimp[[13]][1:19,1:2],
      varimp[[14]][1:19,1:2],
      varimp[[15]][1:19,1:2],
      varimp[[16]][1:19,1:2],
      varimp[[17]][1:19,1:2],
      varimp[[18]][1:19,1:2],
      varimp[[19]][1:19,1:2],
      varimp[[20]][1:19,1:2],
      varimp[[21]][1:19,1:2],
      varimp[[22]][1:19,1:2],
      varimp[[23]][1:19,1:2],
      varimp[[24]][1:19,1:2],
      varimp[[25]][1:19,1:2],
      varimp[[26]][1:19,1:2],
      varimp[[27]][1:19,1:2],
      varimp[[28]][1:19,1:2],
      varimp[[29]][1:19,1:2],
      varimp[[30]][1:19,1:2],
      varimp[[31]][1:19,1:2]) -> varimp.df

View(varimp.df)
varimp.df
```
even there is more than 50 PCNM variables, they do not actively contribute Model performance
Most of important PCNM variables were from 1:10. 
and among 1:10, PCNM 1,2,3 effect alot.
maybe because of clustering?

Try with all climate variables.
load old climate 19 datas
```{r}
climatedata <- readr::read_rds("data/newdata/data.amphibian.rds")
climatedata[c(5,9,10,23,25,26,27,29,31,33,34,42,44,45,49)] <- NULL # make 35 same as pcnm
climatedata[c(11, 21, 25, 31)] <- NULL

for(i in 1:31){
climatedata[[i]]@data %>% dplyr:::select(., 1:19) %>% cbind(pcnm.df[[i]]) -> climatedata[[i]]@data}
                                        #all variables with 50 PCNM

```


add to sample bg for glm error
```{r}
data3 <- map(climatedata, addSamplesToBg)
t.t3 <- list()
for (i in 1:31){
  t.t3[[i]] <- trainValTest(data3[[i]], 
                           test = 0.2, 
                           only_presence = TRUE, 
                           seed = 1)}
fold3 <- map(t.t3, rnd4k)


```

```{r}
model_rndcv4k_amphibian <- future_map2(t.t3, 
                                    fold3, 
                                    maxnet.train, 
                                    .options = furrr_options(seed = TRUE),
                                    .progress = T)
```

go for 2nd varimp
```{r}
varimp2 <- future_map(model_rndcv4k_amphibian, varImp)

varimp.df2 <- data.frame(matrix(ncol = 62, nrow = 19))
cbind(varimp2[[1]][1:19,1:2],
      varimp2[[2]][1:19,1:2],
      varimp2[[3]][1:19,1:2],
      varimp2[[4]][1:19,1:2],
      varimp2[[5]][1:19,1:2],
      varimp2[[6]][1:19,1:2],
      varimp2[[7]][1:19,1:2],
      varimp2[[8]][1:19,1:2],
      varimp2[[9]][1:19,1:2],
      varimp2[[10]][1:19,1:2],
      varimp2[[11]][1:19,1:2],
      varimp2[[12]][1:19,1:2],
      varimp2[[13]][1:19,1:2],
      varimp2[[14]][1:19,1:2],
      varimp2[[15]][1:19,1:2],
      varimp2[[16]][1:19,1:2],
      varimp2[[17]][1:19,1:2],
      varimp2[[18]][1:19,1:2],
      varimp2[[19]][1:19,1:2],
      varimp2[[20]][1:19,1:2],
      varimp2[[21]][1:19,1:2],
      varimp2[[22]][1:19,1:2],
      varimp2[[23]][1:19,1:2],
      varimp2[[24]][1:19,1:2],
      varimp2[[25]][1:19,1:2],
      varimp2[[26]][1:19,1:2],
      varimp2[[27]][1:19,1:2],
      varimp2[[28]][1:19,1:2],
      varimp2[[29]][1:19,1:2],
      varimp2[[30]][1:19,1:2],
      varimp2[[31]][1:19,1:2]) -> varimp.df2

View(varimp.df2)
varimp.df2
```

mostly PCNM 1 take everything... 

what will happen if PCNM 1 is excluded?

```{r}

t.t3wo1 <- t.t3
for(i in 1:length(t.t3)){
  t.t3wo1[[i]][[1]]@data <- t.t3[[i]][[1]]@data[,-20] 
}

model_wo1 <- future_map2(t.t3wo1, 
                                    fold3, 
                                    maxnet.train, 
                                    .options = furrr_options(seed = TRUE),
                                    .progress = T)
```

go for 3rd varimp
```{r}
varimp3 <- future_map(model_wo1, varImp)

varimp.df3 <- data.frame(matrix(ncol = 62, nrow = 19))
cbind(varimp3[[1]][1:19,1:2],
      varimp3[[2]][1:19,1:2],
      varimp3[[3]][1:19,1:2],
      varimp3[[4]][1:19,1:2],
      varimp3[[5]][1:19,1:2],
      varimp3[[6]][1:19,1:2],
      varimp3[[7]][1:19,1:2],
      varimp3[[8]][1:19,1:2],
      varimp3[[9]][1:19,1:2],
      varimp3[[10]][1:19,1:2],
      varimp3[[11]][1:19,1:2],
      varimp3[[12]][1:19,1:2],
      varimp3[[13]][1:19,1:2],
      varimp3[[14]][1:19,1:2],
      varimp3[[15]][1:19,1:2],
      varimp3[[16]][1:19,1:2],
      varimp3[[17]][1:19,1:2],
      varimp3[[18]][1:19,1:2],
      varimp3[[19]][1:19,1:2],
      varimp3[[20]][1:19,1:2],
      varimp3[[21]][1:19,1:2],
      varimp3[[22]][1:19,1:2],
      varimp3[[23]][1:19,1:2],
      varimp3[[24]][1:19,1:2],
      varimp3[[25]][1:19,1:2],
      varimp3[[26]][1:19,1:2],
      varimp3[[27]][1:19,1:2],
      varimp3[[28]][1:19,1:2],
      varimp3[[29]][1:19,1:2],
      varimp3[[30]][1:19,1:2],
      varimp3[[31]][1:19,1:2]) -> varimp.df3

View(varimp.df3)
varimp.df3
```

